---
title: "Congressional Committee Influence"
#subtitle: ""
author: "Ryan Bell, Stefani Langehennig, & Scott Adler"
institute: "2022 Midwest Political Science Association Conference"
date: "10 April 2022"
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, "ninjutsu"]
    lib_dir: libs
    nature:
      highlightStyle: solarized-light
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(base_color = "#2F4F4F",
  header_font_google = google_font("Yanone Kaffeesatz","200","300","400","500","600","700"),
  text_font_google   = google_font("Roboto", "300", "300i","400","500"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "125%", 
  colors = c(
  red = "#f34213",
  purple = "#3e2f5b",
  orange = "#ff8811",
  green = "#136f63",
  white = "#FFFFFF",
  gold = "#FFD700",
  crimson = "#8B0000"
),
extra_css = list(
    ".remark-slide table" = list("display" = "table",
                   "width" = "80%",
                   "text-align" = "left"),
    ".remark-slide-number" = list("display" = "%current%"),
    ".strong" = list("font-weight" = "400"),
    ".big" = list("font-size" = "350%",
                  "font-family" = "Yanone Kaffeesatz",
                  "font-weight"="400"),
    ".small" = list("font-size" = "80%"),
    ".large" = list("font-size" = "150%"))
)

```

# Agenda
- Motivation
- Data
- Trends
- Conclusions

---

class: left, bottom, inverse
.big[Motivation]

---

# Committee Policy Influence

something here

---

class: left, bottom, inverse
.big[Data]

---

# United States Code (USC)

something here

---

# Committee Influence Score

---

class: left, bottom, inverse
.big[Trends]

---

# Policy Areas Attributed to Sections

something here

---

# Distribution of Committee Influence Over Time

figures here

---
# Distribution of Committee Influence Over Time

table of score comparison here?


---

class: left, bottom, inverse
.big[Conclusions]

---

something here

---

class: left, bottom, inverse
.big[Thank you! Questions?]


